DATA 621 - Business Analytics and Data Mining

### 2020-11-26 HW5/HW5-Group2.Rmd
Create predictions, rename, and push PDF

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
<!-- Assignment -->
```{r loadData}
```
<!-- Data Exploration -->
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
<!-- Data Preparation -->
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m2clean}
```
```{r model3impute}
```
<!-- Build Models -->
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```
```{r m1PvarImp}
```
```{r m1NBTrain}
```
```{r m1NBTable}
```
```{r m1NBvarImp}
```
```{r m1PNB}
```
```{r m2poisson}
```
```{r m2PTable}
```
```{r m2PFitCheck}
```
```{r m1MLRFit}
```
```{r m1MLRTable}
```
```{r m2NBTrainBase}
```
```{r m2NBTrain}
```
```{r m2MLTrainBase}
```
```{r m2MLTrain}
```
<!-- Select Models -->
```{r compTable}
```
```{r m1TestProcess}
```
```{r m1PTest}
```
```{r m2TestProcess}
```
```{r m2PTest}
```
```{r m1NBTest}
```
```{r m2NBTest}
```
```{r m1MLRTest}
```
```{r m2MLTest}
```
```{r modelTestResults}
```

>>>>

```{r readEval}
# Read evaluation but not "IN" since that's dropped right away
m2eval <- fread(paste0(urlRemote, pathGithub, fileEval), drop = 'IN')
nobsE <- dim(DT)[[1]]
```

With `r nobsE` observations in the evaluation set, the predicted cases for each
row will not be printed, rather some summary statistics and a histogram of the
evaluations will be shown. The actual predictions are available in the
`m2evalP` data object, as seen in the CODE APPENDIX.

```{r processEval}
# Process evaluation file as per zero-inflated Poisson model 2
m2eval[,c(2:8,11:12)] <- abs(m2eval[,c(2:8,11:12)])
m2eval$STARS[is.na(m2eval$STARS)] <- 0
set.seed(525)
m2eval.impute <- mice(m2eval, method = 'pmm', print = FALSE)
m2eval <- complete(m2eval.impute)
m2eval.r <- m2eval$TARGET
m2eval.p <- m2eval[, -1]
pre.process <- preProcess(m2eval.p, method = c("YeoJohnson"))
m2eval.p <- predict(pre.process, m2eval.p)
m2eval[, c(2:13, 15)] <- m2eval.p[, c(1:12, 14)]

# Predict Cases
m2evalP = as.data.frame(round(predict(m2.fpmodel, newdata = m2eval)))
colnames(m2evalP) <- 'Cases'
kable(table(m2evalP), caption = "Predicted Cases")
ggplot(m2evalP, aes(x = Cases)) +
  geom_histogram(binwidth = 1, center = 0,
                 fill = 'firebrick4', color = 'black') +
  scale_x_continuous(breaks = 0:8) +
  ggtitle("Histogram of Predicted Cases")
```

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
<!-- Assignment -->
```{r loadData}
```
<!-- Data Exploration -->
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
<!-- Data Preparation -->
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m2clean}
```
```{r model3impute}
```
<!-- Build Models -->
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```
```{r m1PvarImp}
```
```{r m1NBTrain}
```
```{r m1NBTable}
```
```{r m1NBvarImp}
```
```{r m1PNB}
```
```{r m2poisson}
```
```{r m2PTable}
```
```{r m2PFitCheck}
```
```{r m1MLRFit}
```
```{r m1MLRTable}
```
```{r m2NBTrainBase}
```
```{r m2NBTrain}
```
```{r m2MLTrainBase}
```
```{r m2MLTrain}
```
<!-- Select Models -->
```{r compTable}
```
```{r m1TestProcess}
```
```{r m1PTest}
```
```{r m2TestProcess}
```
```{r m2PTest}
```
```{r m1NBTest}
```
```{r m2NBTest}
```
```{r m1MLRTest}
```
```{r m2MLTest}
```
```{r modelTestResults}
```
<!-- Predictions -->
```{r readEval}
```
```{r processEval}
```
